Final Report: Scenario 2 - MPX in the EU

### 2022-12-06 Final Report: Scenario 2 - MPX in the EU.Rmd
Edited figure1,2,3

```{r, echo=FALSE}
euro_mpx_cases %>% 
  ggplot(., aes(x = floor_month, y = cases_grouped_monthly)) +
  geom_bar(aes(fill = EU_region), stat = "identity") +
  theme_minimal() +
  labs(title = "Monthly Cases of Monkeypox in Europe", 
       tag = "Figure 1",
       x = "Month (2022)", 
       y = "Monkeypox Cases") +
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft") 
```

@@

```{r, echo=FALSE}
euro_mpx_cases <- inner_join(euro_mpx_cases, Table_1.1, by= "EU_region") %>%
  group_by(floor_month) %>%
  mutate(Total_Euro_cases_monthly = sum(cases_grouped_monthly)) %>%
  mutate(Total_euro_pop = sum(country_pop_2022)) 
graph1 <- euro_mpx_cases %>%
  select(floor_month, cases_grouped_monthly, EU_region, sum_region_cases.x, Total_region_pop,
         Total_Euro_cases_monthly, Total_euro_pop) %>%
  group_by(floor_month, EU_region) %>%
  mutate(region_monthly_cases = sum(cases_grouped_monthly)) %>% ungroup() %>%
  mutate("monthly_rate_region" = round((region_monthly_cases/Total_region_pop * 100000),2))
ggplot(data=graph1, aes(x=floor_month, y=monthly_rate_region, group= EU_region)) +
  geom_line(aes(color=EU_region)) +
  geom_point() +
  geom_label(label= graph1$monthly_rate_region, nudge_y = 0.1) +
  theme_minimal() +
  labs(title = "Rate of Monkeypox Infections", 
       tag = "Figure 2",
       x = "Month (2022)", 
       y = "Monkeypox Rate (per 100k)") +
    theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft") 
```

@@

demo_data %>% 
  ggplot(., aes(x = COUNTRY_CODE, y = age_cat_pct)) +
  geom_bar(aes(fill = AGE), stat = "identity") +
  theme_minimal() +
  labs(title = "Age Distribution Among Countries with Monkeypox Cases",
       subtitle = "Countries with at least 100 confirmed cases",
       tag = "Figure 3",
       x = "Country", 
       y = "Percentage") +
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft")

>>>>

```{r, echo=FALSE}
euro_mpx_cases1.5 <- euro_mpx_cases %>%
  select(floor_month, EU_region, cases_grouped_monthly) %>%
  group_by(floor_month, EU_region) %>%
  summarize(cases_grouped_monthly = sum(cases_grouped_monthly))

euro_mpx_cases1.5 %>%
  ggplot(., aes(x = floor_month, y = cases_grouped_monthly)) +
  geom_bar(aes(fill = EU_region), stat = "identity") +
  theme_minimal() +
  labs(title = "Monthly Cases of Monkeypox in Europe", 
       tag = "Figure 1",
       x = "Month (2022)", 
       y = "Monkeypox Cases") +
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft")
```

@@

```{r, echo=FALSE}
euro_mpx_cases <- inner_join(euro_mpx_cases, Table_1.1, by= "EU_region") %>%
  group_by(floor_month) %>%
  mutate(Total_Euro_cases_monthly = sum(cases_grouped_monthly)) %>%
  mutate(Total_euro_pop = sum(country_pop_2022)) 
graph1 <- euro_mpx_cases %>%
  select(floor_month, cases_grouped_monthly, EU_region, sum_region_cases.x, Total_region_pop,
         Total_Euro_cases_monthly, Total_euro_pop) %>%
  group_by(floor_month, EU_region) %>%
  mutate(region_monthly_cases = sum(cases_grouped_monthly)) %>% ungroup() %>%
  mutate("monthly_rate_region" = round((region_monthly_cases/Total_region_pop * 100000),2))
ggplot(data=graph1, aes(x=floor_month, y=monthly_rate_region, group= EU_region)) +
  geom_line(aes(color=EU_region)) +
  geom_point() +
  geom_text(label= graph1$monthly_rate_region, nudge_y = 0.1, check_overlap = T) +
  theme_minimal() +
  labs(title = "Rate of Monkeypox Infections", 
       tag = "Figure 2",
       x = "Month (2022)", 
       y = "Monkeypox Rate (per 100k)") +
    theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft")
```

@@

demo_data %>% 
  ggplot(., aes(x = COUNTRY_CODE, y = age_cat_pct)) +
  geom_bar(aes(fill = AGE), stat = "identity") +
  geom_text(aes(label= age_cat_pct), position=position_stack(vjust=0.5), size=2.5) +
  theme_minimal() +
  labs(title = "Age Distribution Among Countries with Monkeypox Cases",
       subtitle = "Countries with at least 100 confirmed cases",
       tag = "Figure 3",
       x = "Country", 
       y = "Percentage") +
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.ticks.x = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size = 14),
        legend.title = element_blank(),
        plot.tag.position = "bottomleft")
